\mireval{}

### 2014-05-09 paper/paper.tex
Removing redundancy

Pattern discovery involves the identification of musical patterns (i.e. short fragments or melodic ideas that repeat at least twice) both from audio and symbolic representations.
The metrics used to evaluation pattern discovery systems attempt to quantify the ability of the algorithm to not only determine the presents pattern in a piece, but also to find all of their occurrences.
Given the novelty of this task (the first year it appeared in MIREX was 2013), the evaluation metrics are likely to be modified in further editions.
Nonetheless, Collins compiled all previously existent metrics and proposed novel ones \cite{Collins2013}, which resulted in 19 different scores, each one implemented in \mireval{}:
\textbf{Standard F-measure, Precision, and Recall}, where an estimated pattern is considered correct only if it matches (up to translation) a reference prototype pattern;
\textbf{Establishment F-measure, Precision, and Recall}, which computes the number of reference patterns that were successfully found, no matter how many occurrences were found;
\textbf{Occurrence F-measure, Precision, and Recall}, which measures whether an algorithm is able to retrieve all occurrences of a pattern;
\textbf{Three-layer F-measure, Precision, and Recall}, which capture both the establishment of the patterns and the occurrence retrieval in a single set of scores;
and the \textbf{First $N$ patterns metrics}, where the target proportion establishment recall and three-layer precision analyzing the first $N$ patterns only, which measures the ability of the algorithm to sort the identified patterns based on their relevance.

@@

\subsection{Weighted Chord Symbol Recall}
For reference, we compare our chord evaluation against the results provided from MIREX 2013.
Though the \textbf{Root} comparison falls well within our accuracy tolerance, the other four comparison rules exhibit non-negligible discrepancies that warrant justification.
Based on our current understanding, implementation differences are caused by two main sources of ambiguity.
%Some interval mappings aren't well-defined.
First, we find some chord labels in the MIREX reference annotations lack well-defined, i.e. singular, mappings into a comparison space. 
One such example is $D:maj(*1)/\#1$.
While the quality shorthand indicates ``major'', the asterisk implies the root is omitted and thus it is unclear whether $D:maj(*1)/\#1==D:maj1$.
%Some chords get dropped in different scenarios, and we can't replicate the logic. 
Second, and more importantly, such chords are likely ignored during evaluation, and we are unable to replicate the exact exclusion logic used by MIREX. 
This has proven to be particularly difficult in the two inversion rules, and manifests in Table \ref{tab:comparison}. 
For example, it seems as though $Bb:maj(9)/9$ was \emph{not} excluded from the MIREX evaluation, contradicting the description provided online.
This chord alone causes an observable difference between the results of our implementation and previously reported results.

>>>>

Pattern discovery involves the identification of musical patterns (i.e. short fragments or melodic ideas that repeat at least twice) both from audio and symbolic representations.
The metrics used to evaluation pattern discovery systems attempt to quantify the ability of the algorithm to not only determine the presents pattern in a piece, but also to find all of their occurrences.
Given the novelty of this task (the first year it appeared in MIREX was 2013), the evaluation metrics are likely to be modified in further editions.
Nonetheless, Collins compiled all previously existent metrics and proposed novel ones \cite{Collins2013}, which resulted in 19 different scores, each one implemented in \mireval{}:
\textbf{Standard F-measure, Precision, and Recall}, where an estimated prototype pattern is considered correct only if it matches (up to translation) a reference prototype pattern;
\textbf{Establishment F-measure, Precision, and Recall}, which computes the number of reference patterns that were successfully found, no matter how many occurrences were found;
\textbf{Occurrence F-measure, Precision, and Recall}, which measures whether an algorithm is able to retrieve all occurrences of a pattern;
\textbf{Three-layer F-measure, Precision, and Recall}, which capture both the establishment of the patterns and the occurrence retrieval in a single set of scores;
and the \textbf{First $N$ patterns metrics}, where the target proportion establishment recall and three-layer precision analyzing the first $N$ patterns only, which measures the ability of the algorithm to sort the identified patterns based on their relevance.

@@

\subsection{Weighted Chord Symbol Recall}
The non-negligible average relative changes seen in the chord metrics are caused by two main sources of ambiguity.
%Some interval mappings aren't well-defined.
First, we find some chord labels in the MIREX reference annotations lack well-defined, i.e. singular, mappings into a comparison space. 
One such example is $D:maj(*1)/\#1$.
While the quality shorthand indicates ``major'', the asterisk implies the root is omitted and thus it is unclear whether $D:maj(*1)/\#1==D:maj1$.
%Some chords get dropped in different scenarios, and we can't replicate the logic. 
Second, and more importantly, such chords are likely ignored during evaluation, and we are unable to replicate the exact exclusion logic used by MIREX. 
This has proven to be particularly difficult in the two inversion rules, and manifests in Table \ref{tab:comparison}. 
For example, it seems as though $Bb:maj(9)/9$ was \emph{not} excluded from the MIREX evaluation, contradicting the description provided online.
This chord alone causes an observable difference between the results of our implementation and previously reported results.
